Figures

### 2020-01-24 manuscript/figures.Rmd
rebuild

@@

@@

```{r 01_geometry_points, fig.cap = "Caption.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_geometry-1.pdf")
```

```{r 01_geometry_map, fig.cap = "Green points show the 'visual center' of the lake. Red points show the true deepest point of a lake.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_geometry-2.pdf")
```

>>>>

```{r constrasts_distance, fig.cap = "Contrasting distance from shore to the deepest point in the lake and distance to the lake visual center for natural lakes and reservoirs.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_geometry-2.pdf")
```

@@

```{r 02_depth_oliver-2, fig.cap = "Reproduction of Oliver 2016 using LAGOSUS data in LAGOSNE footprint.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/02_depth_oliver-2.pdf")
```

```{r 02_depth_oliver-1, fig.cap = "Reproduction of Oliver 2016 using LAGOSUS data in LAGOSNE footprint.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/02_depth_oliver-1.pdf")
```

```{r 02_depth_oliver-4, fig.cap = "Oliver 2016 observed versus predicted.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/02_depth_oliver-4.pdf")
```

@@

```{r 01_geometry_points, fig.cap = "Distance to deepest point versus distance to lake visual center.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_geometry-1.pdf")
```

```{r 01_geometry_map, fig.cap = "Green points show the 'visual center' of the lake. Red points show the true deepest point of a lake.", warning=FALSE, echo = FALSE, eval=TRUE}
knitr::include_graphics("../figures/01_geometry-3.pdf")
```
